Brief Announcement: An Improved Lower Bound for Dynamic Balanced Graph Partitioning

### 2020-02-17 paper/paper.tex
Fix

 useful sentences. This section is TODO}
An algorithm that  keeps all components collocated is \emph{component-respecting}.
%
A \emph{component} is a subset of frequently communicating nodes.   ly,                                                   ,every node is trivially a \emph{singleton} component.
We grow components similar fashion to previous approaches~\cite{repartition-disc}.
which proved to be an effective techique for mimi                                                                it always keep.
That is,
if the algorithm needs to move a node,
it moves the whole component containing the node to the sameemph{component -respecting}, i.e., it maintains the invariant that nodes of each component are collocated in the same cluster.
%We say that the request $(u,v)$ is \emph{external}, if the algorithm is in the configuration, where $u$ and $v$ are located at different clusters.
%
This is achieved by opting a sequence of  partitions (a.k.a.~configurations)
such that frequently communicating nodes (from different clusters)
are relocated to the same cluster before they inflict too much communication cost.
A \emph{reconfiguration} (i.e.,\re-partitioning) is performed by
 migrating) nodes betwen clusters at a cost.   ,s to jointly minimize communication and migration costs while serving the sequence.

>>>>

An algorithm that  keeps all components collocated is \emph{component-respecting}.
%
A \emph{component} is a subset of frequently communicating nodes.   ly,                                                   ,every node is trivially a \emph{singleton} component.
We grow components similar fashion to previous approaches~\cite{repartition-disc}.
which proved to be an effective techique for mimi                                                                it always keep.
That is,
if the algorithm needs to move a node,
it moves the whole component containing the node to the sameemph{component -respecting}, i.e., it maintains the invariant that nodes of each component are collocated in the same cluster.
%We say that the request $(u,v)$ is \emph{external}, if the algorithm is in the configuration, where $u$ and $v$ are located at different clusters.
%
This is achieved by opting a sequence of  partitions (a.k.a.~configurations)
such that frequently communicating nodes (from different clusters)
are relocated to the same cluster before they inflict too much communication cost.
A \emph{reconfiguration} (i.e., re-partitioning) is performed by
 migrating) nodes betwen clusters at a cost.   ,s to jointly minimize communication and migration costs while serving the sequence.
